Collocated Snapshot Backup with VM-Centric Deduplication in the Cloud

### 2013-09-26 snapshot_system/fast14_architecture.tex
update

\subsection{ Components of a cluster node } 
As depicted in Figure~\ref{fig:arch_vm}, 
there are four key service components running on each cluster
node  for supporting backup and deduplication: 
1) a virtual block device driver, 2) a snapshot deduplication agent,
3) a snapshot store client to store  and access snapshot data,
and 4)  a PDS client to support PDS metadata access.

@@

\subsection{A VM-centric snapshot store for backup data}
\label{sect:store}
We build the snapshot storage on the top of a distributed file system.
Following the VM-centric idea for the purpose of fault isolation,
each VM has its own snapshot store, containing new data chunks which are considered
to be non-duplicates.
There is also a special store containing all PDS chunks shared among different VMs.
As shown in Figure~\ref{fig:as_arch}, we explain the data structure of the snapshot stores as follows.
\begin{figure}[htbp]
  \centering
  \includegraphics[width=2.75in]{images/sstore_arch}
  \caption{Data structure of a VM snapshot store.}
  \label{fig:as_arch}
\end{figure}

>>>>

\subsection{ Components of a Cluster Node } 
As depicted in Figure~\ref{fig:arch_vm}, 
there are four key service components running on each cluster
node  for supporting backup and deduplication: 
1) a virtual block device driver, 2) a snapshot deduplication agent,
3) a snapshot store client to store  and access snapshot data,
and 4)  a PDS client to support PDS metadata access.

@@

\subsection{A VM-centric Snapshot Store for Backup Data}
\label{sect:store}
We build the snapshot storage on the top of a distributed file system.
Following the VM-centric idea for the purpose of fault isolation,
each VM has its own snapshot store, containing new data chunks which are considered
to be non-duplicates.
There is also a special store containing all PDS chunks shared among different VMs.
As shown in Figure~\ref{fig:as_arch}, we explain the data structure of the snapshot stores as follows.
\begin{figure}[htbp]
  \centering
  \includegraphics[width=2.75in]{images/sstore_arch}
  \caption{Data structure of a VM snapshot store.}
  \label{fig:as_arch}
\end{figure}
